\begin{acknowledgements}  

This year has been the most difficult year of my life for many reasons, and I want to thank all the people who have helped motivate me to keep going when I truly felt like giving up for the first time in my life. \\
Firstly I want to acknowledge the incredible patience, support and encouragement my thesis supervisor, Dr Dries Verstraete, has given me this year. From replying to emails at ridiculous night hours to motivating me when I was at my absolute lowest. Thank you so much, and I am so grateful to have had the opportunity to do this thesis under your guidance.  \\
To Benjamin Van Magil, thank you for taking time out of your schedule to help me learn more about FreeCAD and the design decisions you've made yourself when designing 3D printed models. For finalising the model design with me and assisting in the wind tunnel along with some of the other PhD students, thank you so much! \\
To Gabby Papadopoulos, thank you for letting me visit every day, being there for me, and helping me process all that I've been through this year. Our daily runs and midnight conversations helped me process so many different things. This thesis would have never made it to fruition without you. Thank you.\\
To Irina Tyan, her partner Ben, and her parents, who have given me so much support during the most incredibly stressful time of my life. You made an impossible situation something that helped me grow as a person, and I will forever appreciate the kindness and support you have all shown.\\
To Alex, who dragged me out of the house when I barely had the energy to get up in the morning. Thank you for encouraging me to keep going and giving me little nuggets of advice when everything was too overwhelming. Your advice helped me break this into more manageable chunks of work until I finally reached the end. 



\end{acknowledgements}